SETI in the Spatial-Temporal Survey Domain

### 2019-04-17 paper/ms.tex
section 3 written thru

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%
\title{SETI in the Optical Spatial-Temporal Domain}

\shorttitle{Spatial-Temporal SETI}
\shortauthors{Davenport}

@@

The SETI conundrum has always been not only ``{\it What should we look for?}'', but  also {\it ``When and where to look?}''. 
While \citet{wright2018c} suggest the completeness of our search of the ``cosmic haystack'' at radio wavelengths is akin to the ratio of a swimming pool compared to the Earth's ocean's ($\sim$10$^{-20}$), SETI at optical wavelengths is surely many orders of magnitude less complete. However, new wide-field time domain surveys will enable us to greatly expand our search in two key dimensions of parameter space: 1) collectively observing nearly the entire night sky, and 2) providing time resolved monitoring over many years.

@@

Several types of signals have been suggested that may be viable for use with optical surveys. For example, \citet{villarroel2016} searched two wide field, single-epoch optical surveys for objects ``disappearing''  over decades timescales. \citet{lacki2019} outline a method to search for specular reflections of interplanetary objects, particularly in wide field surveys. \citet{arnold2005} describe the the observable signature of transits from ostensibly artificial objects, which could be searched for with exoplanet transit surveys.

Here I list a few general classes of technosignature signals that may be well suited for developing new detection algorithms around:

\begin{itemize}
\item unusual variability profiles or statistical distributions -- either on short timescales (e.g. Boyajian's Star) or long timescales (e.g. VASCO)
\item spatial correlations of events or phenomena -- e.g. coordination of transiting systems, or rebroadcasting events such as novae along the ``SETI ellipse'' \citep{makovetskii1977,lemarchand1994,tarter2001,shostak2004}
\item spatial density or distribution -- e.g. an over density of phenomena, such as within the Earth Transit Zone \citep{heller2016}
\item unnatural patterns, particularly patterns of otherwise normal variability -- e.g. a prime or fibonacci sequence
\end{itemize}

>>>>

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%
\title{SETI in the Spatial-Temporal Survey Domain}

\shorttitle{Survey SETI}
\shortauthors{Davenport}

@@

The SETI conundrum has always been not only ``{\it What should we look for?}'', but  also {\it ``When, where, and how to look?}''. 
While \citet{wright2018c} suggest the completeness of our search of the ``cosmic haystack'' at radio wavelengths is akin to the ratio of a swimming pool compared to the Earth's ocean's ($\sim$10$^{-20}$), SETI at optical wavelengths is surely many orders of magnitude less complete. However, new wide-field time domain surveys will enable us to greatly expand our search in two key dimensions of parameter space: 1) collectively observing nearly the entire night sky, and 2) providing time resolved monitoring over many years.

@@

Several types of signals have been suggested that may be viable for use with optical surveys. For example, \citet{villarroel2016} searched two wide field, single-epoch optical surveys for objects ``disappearing''  over decades timescales. \citet{lacki2019} outline a method to search for specular reflections of interplanetary objects, particularly in wide field surveys. \citet{arnold2005} describe the the observable signature of transits from artificial objects, which could be searched for with exoplanet transit surveys. \citet{kipping2016} find that exoplanet transits could be hidden or ``cloaked'' to an observer by using directed laser emission.

Here I describe a few general classes of technosignature signals that may be well suited to developing new detection algorithms for spatial-temporal surveys:

\begin{enumerate}
\item {\bf Unusual variability profiles or statistical distributions of fluxes }-- either on short timescales such as Boyajian's Star \citep{boyajian2015}, or long timescales such as disappearing stars \citep{villarroel2016} or occasionally missing transits \citep{kipping2016}
%
\item {\bf Spatial correlations of events or phenomena }-- e.g. coordination of transiting systems, or rebroadcasting events such as novae along the ``SETI ellipse'' \citep{makovetskii1977,lemarchand1994,tarter2001,shostak2004}
%
\item {\bf Spatial over-density or distribution} -- e.g. an over-density of a given phenomena, such as within the Earth Transit Zone \citep{heller2016}
%
\item {\bf Unnatural patterns} -- particularly patterns of otherwise normal astrophysical variability, such as broadcasting a prime or fibonacci sequence of transits \citep{wright2016}.
%
\end{enumerate}
